Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-22 paper/paper.tex
case study completed

We can still use samples and summary statistics with BBVB to
approximate the posterior distribution, however variational
inferences approximates the posterior by known distributions,
and we can directly retrieve the distribution parameters.

>>>>

We can still use samples and summary statistics with BBVB to
approximate the posterior distribution, however variational
inference approximates the posterior by known distributions,
and we can directly retrieve the distribution parameters.
